\documentclass[LSE,toc]{lsstdoc}

%% Journal abbreviations

\title[LSST Science Platform]{LSST Science Platform Vision Document}

\author{
M.~Juri\'c,
D.~Ciardi,
and
G.P.~Dubois-Felsmann
}

\setDocRef{LSE-319}
\date{2017-09-11}
\setDocUpstreamLocation{\url{https://github.com/lsst-dmsst/LSE-319}}

\setDocAbstract{%
This document defines and describes the ``LSST Science Platform'', a set of integrated web applications and services deployed at the LSST Data Access Centers (DACs) through which the scientific community will access, visualize, subset and perform next-to-the-data analysis of the data collected by the Large Synoptic Survey Telescope (LSST).
\\

These services can be broken down to three different aspects: a web \textbf{Portal}, designed to provide essential data access and visualization services through a simple-to-use website, a \textbf{JupyterLab} environment, that will provide a Jupyter Notebook-like interface enabling next-to-the-data analysis, and an extensive set of \textbf{Web APIs} that the users will be able to use to remotely examine the LSST data set using tools they're already familiar with.
\\

This document lays out the high-level vision for the aforementioned aspects and some associated backend services. It is intentionally brief, and meant to generally guide the flow-down of requirements and development product specifications, prioritization, and plans for the Agile development of the relevant elements of the DM system.

}

% Change history defined here. Will be inserted into
% correct place with \maketitle
% OLDEST FIRST: VERSION, DATE, DESCRIPTION, OWNER NAME
\setDocChangeRecord{%
\addtohist{}{2017-05-22}{Initial version}{Mario Juric}
\addtohist{1.0}{2017-09-11}{Approved in \href{https://project.lsst.org/groups/ccb/node/1762}{LCR-1013}}{Tim~Jenness}
%\addtohist{2}{yyyy-mm-dd}{Future changes}{Future person}
}

\begin{document}

% Create the title page
% Table of contents will be added automatically if "toc" class option
% is used.
\maketitle

\section{Preface}

The purpose of this document is to lay out the high-level vision for the \textbf{LSST Science Platform (LSP)}, a set of web applications and services through which the the scientific community will to access, visualize, interact with, and analyze LSST data holdings. With its companion document -- the Data Products Definition Document (\DPDD) -- it defines the high-level vision for LSST's end-user deliverables.
\\

To a future LSST user, this document should illustrate what will be made available to the science community through the LSST Data Access Centers. To LSST builders, it provides direction on how to flow down the LSST System Requirements Document (\LSR) to Data Management requirements (\DMSR) as they pertain to the end-user services provided at the LSST Data Access Centers.
\\

Though under strict change control, this is a \textbf\emph{living document}. LSST will undergo a period of construction  and commissioning lasting no less than seven years, followed by a decade of survey operations. To ensure their continued scientific adequacy, the high-level vision for LSST Science Platform will be periodically reviewed and updated.

\clearpage

\include{Introduction}
\include{user}
\include{backend}
\include{methodology}
\include{evolution}
\clearpage

\bibliography{lsst}

\end{document}
